On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-05-25 documents/paper.tex
4-pole LO

\title{On the application of microwave-acoustic resonant viral inactivation
\thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
\date{May 2020}
\author{Based primarily on exceptional work by }

@@

Brief:

Aims:
We extend this landmark work rather trivially by:
\begin{itemize}
  \item Establishing the time dependence of inactivation
  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
  \item Discussing the biological basis for the safety of the device
  \item Showing that the deviation from the expected theshold could be explained by variance in the 
\end{itemize}
\end{abstract}

@@

[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture. Such a mechanism could perhaps extend the exposure required to break the capsid or membrane. Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the lipid fractures,

@@

\end{itemize}\
%
Generally a third element is also used:
%
\begin{itemize}
\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
\end{itemize}
%
We encountered proximity effects from reflections and near-field coupling off nearby flesh; if this instablity, mode-hopping and de-tuning becomes an issue, it could be mitigated by way of shielding (adding a manufacturing step), or a tight filter around the desired mode.

@@

With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms.

If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].

@@

@@

>>>>

\title{On the application of microwave acoustic resonant viral inactivation
\thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}}
\date{May 2020}
\author{Based primarily on exceptional work by }

@@

We extend this landmark work rather trivially by:

Aims:

\begin{itemize}
  \item Establishing the time dependence of inactivation
  \item Demonstrating a modulation scheme that decreases the inactivation threshold to below current safety levels in surrogate bacteriophage
  \item Demonstrating a prototype emitter in an "electromagnetic mask" form-factor, costing about \$5 in prototype quantities, which can reasonably be produced in 10 million-of quantities
  \item Testing power thresholds in various conditions; biological fluids of various conductivities and pHs
  \item Using a coarse-grained molecular-dynamics simulation to optimize the impulse
  \item Using a virus-in-the-loop optimization with a centrifugal microfluidic system
  \item Discussing the biological basis for the safety of the device
  \item Showing that the deviation from the expected theshold could be explained by variance in the 
\end{itemize}
\end{abstract}

@@

[] found a significant mechanical fatigue effect in phage capsids, where a small strain applied repetitively eventually causes a fracture. Such a mechanism could perhaps extend the exposure required to break the capsid or membrane. Other mechanisms could include some sort of lipid denaturation, requiring an absolute amount of energy absorption to break or twist bonds before the envelope fractures.

@@

\end{itemize}\
%
However, a third element is also required:
%
\begin{itemize}
\item A frequency-selective element that restricts oscillation modes and decreases phase noise.
\end{itemize}
%
Without this element, proximity effects from nearby flesh, startup instablity, mode-hopping, and de-tuning were all encountered.

@@

With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke.

If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters) terminated with a stub to produce a virtual short or open circuit [Seo 2007].

@@

\paragraph{Acknowledgements}\

This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.

Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck. Any comparable dimwit to the author would have accomplished the same under the same conditions.

It is infinitely to be regretted that such equally capable people were stuck in warehouses doing menial 15-hour shifts or assembling smartphones.

Chiefly among the enablers are of course my parents, without which the author would not have existed[] - but who also supported this work financially.

One Very Important Thought

@@

It may be helpful to treat simulations very similarly to IRL experiments.
